Hybrid platforms and bargaining power

### 2024-08-21 src/paper/application.tex
Highlight diff-in-diff idea

This paper aims to contribute to this discussion by examining an important but underexplored aspect of platforms: the bargaining power disparity between the latter and the other market participants, and how this disparity is affected by the platforms' hybrid operation.
I propose an analytically tractable that captures many important aspects of bargaining between one large and a continuum of small players: namely, a hybrid platform facing a continuum of potential entrants.
I show that hybrid operation can indeed have negative welfare consequences for consumers in the presence of bargaining.
This result is particularly striking in this otherwise distortion-free\footnote{
    The platform's hybrid operation does not affect consumer welfare in the benchmark model without bargaining.
} setting. 
The intuition is that hybrid operation increases the platform's bargaining power against the entrant sellers.
This, in turn, leads to a higher entry fee and fewer entrants, resulting in lower consumer surplus.
These observations constitute a so far overlooked aspect of hybrid platforms that policymakers should be aware of.
Due to this model's generality, these results are applicable not only to hybrid platforms, but also to many other settings, such as upstream producers having their own downstream outlets or retailers with private labels.

>>>>

This paper aims to contribute to this discussion by examining an important but underexplored aspect of platforms: the bargaining power disparity between the latter and the other market participants, and how this disparity is affected by the platforms' hybrid operation.
I propose an analytically tractable that captures many important aspects of bargaining between one large and a continuum of small players: namely, a hybrid platform facing a continuum of potential entrants.
In this paper's distortion-free setting with lump-sum entry fees, hybrid platforms are not detrimental to consumer welfare under the usual assumption of the platform setting the entry fee unilaterally.
I show that, in contrast, in the presence of bargaining, hybrid operation can reduce consumer welfare.
The intuition is that hybrid operation increases the platform's bargaining power against the entrant sellers.
This, in turn, leads to a higher entry fee and fewer entrants, resulting in lower consumer surplus.
These observations constitute a so far overlooked aspect of hybrid platforms that policymakers should be aware of.
Due to this model's generality, these results are applicable not only to hybrid platforms, but also to many other settings, such as upstream producers having their own downstream outlets or retailers with private labels.
